### 2018-11-08 Sabanci_talk/Sabanci_talk.tex
New figs added, more work on slides

\documentclass[xcolor=dvipsnames,handout,t]{beamer}
% use handout in document class to stop transitions

@@

\begin{frame}{Gamma-ray bursts}{Most energetic explosions in the universe}
\begin{small}
    \begin{itemize}
      \item Discovered by Vela satellites in 1967
      \uncover<2->\item Non-thermal spectrum: $10-10^4\,$keV
      \uncover<3->{\item Highly energetic $10^{48}-10^{52}\,$ergs 
      \item 1000s detected, $\sim 1$ per day}
      \uncover<4->\item Far away: $z\approx 9.4 \sim 13\,$billion light years!
      \uncover<5->\item Afterglow from X-rays to radio \\
      over timescales of hours to months
      \uncover<6->\item Two types: short and long
      \uncover<7->{\item Short GRBs:\\ 
      mergers of binary neutron stars\\
      \red{GW170817}-\bl{GRB170817A}}
    \end{itemize}
  \end{small}
  \begin{tikzpicture}[overlay,remember picture]
      \onslide<2>\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(3.9cm,1.4cm)}]current page.center) {\includegraphics[height=3.5cm]{figs/GRB_spectrum.jpg}};    
      \onslide<3>\node (img1 )[anchor=center,scale=0.8,opacity=1] at ([shift={(3.8cm,0.9cm)}]current page.center) {\includegraphics[height=3.5cm]{figs/Fermi_GRB_sky2.png}};  
      \onslide<4>\node (img2 )[anchor=center,scale=1,opacity=1] at ([shift={(3.6cm,-0.15cm)}]current page.center) {\includegraphics[height=3.8cm]{figs/GRB_vs_redshift.png}};  % from:1401.5069
      \onslide<5>\node (img3 )[anchor=center,scale=1,opacity=1] at ([shift={(3.4cm,-1.5cm)}]current page.center) {\includegraphics[height=3.5cm]{figs/GRB_afterglow.jpg}}; 
      \onslide<6>\node (img4 )[anchor=center,scale=1,opacity=1] at ([shift={(3.2cm,-2.5cm)}]current page.center) {\includegraphics[height=3.5cm]{figs/GRB_burst_durations.jpg}};    
    \end{tikzpicture}
\end{frame}

\begin{frame}{Neutron Stars}{Most extreme stars in the universe}
  Stellar evolution -> white dwarf, NS -> BH \\
  Density, mass, radius, spin, nuclear equation of state\\
  Tea spoon of neutron star matter trillion tons
\end{frame}

@@

\begin{frame}{Gravitational waves: d.o.f.'s}
$A_{\mu\nu} $ is the polarization tensor.
\begin{itemize}
 \uncover<2->{\item $\{ \bar{h}_{\mu\nu}, A_{\mu\nu} \}$: $4\times4$, symmetric \uncover<3->{$\hspace{1.5cm}\Rightarrow \f{4\times 5}{2}\ \ \ = 10$ d.o.f.}}
 \uncover<4->{\item Gauge condition: $\nabla_\mu \bar{h}^{\mu\nu} =  A_{\mu\nu} k^\nu= 0$ \uncover<5->{$\Rightarrow10-4 = \, 6$ d.o.f.}}
 \uncover<6->{\item Residual gauge freedom \hspace{2.25cm} \uncover<7->{$\Rightarrow 6-4 \ \ = \alert{2}$ \alert{d.o.f.}}}
 %\uncover<7->{\vspace{2mm}\begin{center}$ \bar{h}'_{\mu\nu} = \bar{h}_{\mu\nu} - \xi_{\mu,\nu} - \xi_{\nu,\mu} + \eta_{\mu\nu} \nabla_\alpha \xi^\alpha . $ \end{center}\vspace{2mm}}
\end{itemize}
\uncover<7->{\quad \ Consistent with $\pm 2$ helicities of a \bl{massless} spin 2 boson.\\}
\uncover<8->{$\Rightarrow$ \alert{2} POLARIZATIONS (\alert{transverse}): \uncover<10->{$\begin{array}{l}A_{xx}=-A_{yy} = \red{h_+}  \\ A_{xy}=\ \ A_{yx} = \red{h_\times}  \\ \end{array}$}}
\\
\begin{tikzpicture}[overlay,remember picture]
\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(-3.5cm,-2.5cm)}]current page.center) {\animategraphics[loop,controls,height=2.6cm]{12}{GWs_plus-}{0}{20}};
\node (img1 )[anchor=center,scale=1.,opacity=1] at ([shift={(3.5cm,-2.5cm)}]current page.center) {\animategraphics[loop,controls,height=2.6cm]{12}{GWs_cross-}{0}{20}};
\end{tikzpicture}
\end{frame}

\begin{frame}{Making gravitational waves}{non-spherical, accelerated motion}
  \alert{Inspirals}, GRBs, bumps on neutron stars, supernovae, the Big Bang. \\%  (BICEP 2).\\
  Gravitational-wave luminosity: \alert{quadrupole} radiation (leading-order)
  \begin{center} $ \boxed{\dot{E}=L_\text{GW} = \f{G}{c^5} \langle (\partial_t^3 \bar{Q}_{ij})^2 \rangle}$\\
  \vspace{2mm}
  \begin{small}$ \quad \bar{Q}_{ij} = Q_{ij}-\frac{1}{3}\delta_{ij}Q^k_k, \quad Q^{ij} = \int \rho(t,{\mathbf x})x^i x^j d^3 x $ \end{small} \end{center}
  \onslide<2->{{\bf Binary systems:} 2 points masses in circular orbit.}
  \begin{tikzpicture}[overlay,remember picture]
    \onslide<5->\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(-3.8cm,-2.7cm)}]current page.center) {\animategraphics[loop,controls,height=2.9cm]{12}{Circ_Orb-}{0}{20}};
    \onslide<3->\node (t1 )[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-1.3cm)}]current page.center) {$\mu=m_1 m_2/M^2,\ x(t) = r \cos\Omega t, \ y(t) = r \sin\Omega t $};
    \onslide<4->\node (t2 )[anchor=center,scale=1,opacity=1] at ([shift={(2.25cm,-2.2cm)}]current page.center) {$ Q^{ij} =  2 M\, x^i x^j, \qquad \boxed{\dot{E} = \f{32}{5}\f{G\mu^2}{c^5}r^4 \Omega^6}$};
    \onslide<5->\node (t3 )[anchor=center,scale=1,opacity=1] at ([shift={(2.5cm,-3.2cm)}]current page.center) {Enhancement due to \bl{$e$} (Peters \& Mathews).};
    \onslide<6->\node (t3 )[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-4cm)}]current page.center) {$ \bl{\f{\left(1 + \f{73}{24}e^2+ \f{37}{96} e^4 \right)}{(1-e^2)^{7/2}}}$};
  \end{tikzpicture}
\end{frame}

@@

\begin{frame}{Compact Binary Inspirals}{Newtonian evolution}
 Define \bl{chirp mass} \hspace{1.cm} $\red{M_c} \equiv \mu^{3/5} M^{2/5} = \tfrac{(m_1 m_2)^{3/5}}{(m_1+m_2)^{1/5}}$ \\
 %and symmetric mass ratio\qquad $\nu \equiv \tfrac{\mu}{M} =\tfrac{m_1 m_2}{M^2}$\\
 \vspace{1mm}
 which gives, using Kepler's \bl{third law}: $\Omega^2 = G M r^{-3}=\omega^2/4$   
 \begin{footnotesize}
  $$ \boxed{\dot{E} = \f{32}{5}\f{c^5}{G} \left(\f{G M_c\, \omega}{2c^3}\right)^{10/3}}$$
 \end{footnotesize}\\
%
{\bf Key idea:} \red{energy balance} between $\dot{E}$ and $\dot{E}_b$\\
 %of gravitational binding energy
\quad where $ E_b= -\tfrac{G m_1 m_2}{2r} = -\left(\tfrac{G^2 M_c^5 \omega^2}{32}\right)^{1/3} $
%
\[ 
 \dot{E}(f) = -\dot{E}_b(f) \Longrightarrow \boxed{\red{\dot{f}} = \f{96}{5}\pi^{8/3} \f{(G M_c)}{c^5}^{5/3}\, \red{f^{11/3}} }
 \]
\[
 \red{ \dot{f} \propto f^{11/3}\quad(1)}
\]

\begin{tikzpicture}[overlay,remember picture]
\node[draw, red,thick,minimum width=3cm,minimum height=0.75cm] (b) at (5.9,0.85){};
\end{tikzpicture}

@@

\begin{frame}{Compact Binary Inspirals}
\vspace{-3mm}
Integrate $\dot{f} \sim f^{11/3} \quad \Longrightarrow \quad \int dt \sim \int f^{-11/3}df \quad\Rightarrow\quad t \sim \red{f^{-8/3}}$
\\
\vspace{1mm}
Fix integration constant $\tau = t_\text{coal} - t >0$. \\
\vspace{2mm}
Introduce \red{inspiral time}, i.e, time to BNS \bl{coal}escence
%
\begin{small}
\begin{align}
 \red{\tau_\text{insp}(f)} %&= \f{5}{256\pi}\f{c^5}{(\pi G M_c)^{5/3}} \,{f^{-8/3}}\nn\\
 &\simeq \bl{16.72\,\text{minutes}} \, \left(\f{1.219 M_\odot}{M_c}\right)^{5/3}\,{\left(\f{10\,\text{Hz}}{\red{f}}\right)^{\red{8/3}}\quad \red{(2)}}\nn\hspace{2cm}
\end{align}
\end{small}
Number of GW cycles to coalescence: $\int \tfrac{f}{\dot{f}}df\sim \red{f^{-5/3}}$ %$\int df {f}/\dot{f}$
\begin{small}
\begin{align}
 \red{\mathcal{N}_\text{cyc}(f)} %&=\f{1}{32\pi} \f{c^5}{(\pi G M_c)^{5/3}}\left[ f^{-5/3}-f_\text{max}^{-5/3}\right]\nn \\
 &\approx 1.605\times \bl{10^4}\,\left(\f{1.219 M_\odot}{M_c}\right)^{5/3}{ \left(\f{10\,\text{Hz}}{\red{f}} \right)^{\red{5/3}}}\quad \red{(3)}\nn\hspace{3.2cm}
\end{align}
\end{small}
%
\begin{tikzpicture}[overlay,remember picture]
  \node[draw, red,thick,minimum width=9.2cm,minimum height=1.3cm] (b) at (5.,3.35){};
  \node[draw, red,thick,minimum width=9cm,minimum height=1.3cm] (b) at (4.4,1){};
  \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(3.9cm,-3.2cm)}]current page.center) {\includegraphics[height=3.5cm]{figs/R_of_Tau.pdf}};
\end{tikzpicture}
%
\[ 
\tfrac{\dot{r}}{r}\sim \tfrac{\dot{f}}{f} \Longrightarrow \red{r(\tau)}=r_i \left(\f{\red{\tau}}{\tau_i}\right)^{\red{1/4}} \hspace{4cm}
\]

\begin{frame}{Gravitational waves from BNS}
  TT gauge, multipole, slow-velocity expansions give \todo{add suppl. slide}
  \begin{small}
    \[
    h_{ij}^\text{TT} = \tfrac{2}{D}\tfrac{G}{c^4} \ddot{Q}_{ij}^\text{TT}%(t-z/c)
    \]
    %
    \vspace{-5mm}
    \begin{align*}
    h_+(t) &= h_c(t)\, \left(\f{1+\cos^2\iota}{2}\right)\, \cos[\Phi(t)],\\
    h_\times(t) & =h_c(t)\,\cos\iota \sin[\Phi(t)],
    \end{align*}
  \end{small}
  %
  %
  $\iota =\,$ orbital \bl{inclination}, and
  \vspace{-3mm}
  %
  \begin{small}
    \begin{align*}
    h_c(t) %&=\f{4}{D}\left(\f{G M_c}{c^2}\right)^{5/3}\, \left(\f{\pi f(t)}{c}\right)^{2/3}\nn\\
    &\approx 1.9\times \bl{10^{-23}} \left(\f{40\,\text{Mpc}}{D}\right)\left(\f{M_c}{1.219 M_\odot}\right)^{5/3}\left(\frac{\red{f}}{10\,\text{Hz}}\right)^{\red{2/3}} \nn\\
    \Phi(t) &=\int_{t_i}^t dt' \omega(t') + \text{PN}
    \end{align*}
  \end{small}\\
  %
  Frequency increases as $f^{11/3}$\\
  Amplitude increases as $f^{10/3} $
  %
  %
  \begin{tikzpicture}[overlay,remember picture]
    \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(2.7cm,-3.2cm)}]current page.center) {\includegraphics[height=2.5cm]{figs/Chirp.pdf}};
     \node[anchor=center,scale=1.4,opacity=1] at ([shift={(1cm,-2.4cm)}]current page.center) {\href{https://www.youtube.com/watch?v=CH9JSqUfnSw}{\red{Chirp!}}};
  \end{tikzpicture}
\end{frame}

@@

>>>>

%\documentclass[xcolor=dvipsnames,t]{beamer}
\documentclass[xcolor=dvipsnames,handout,t]{beamer}
% use handout in document class to stop transitions

@@

\begin{frame}{Gamma-ray bursts}{Most energetic explosions in the universe}
\begin{small}
    \begin{itemize}
      \item Discovered by Vela satellites in 1967
      \onslide<2->\item Non-thermal spectrum: $10-10^4\,$keV
      \item Highly energetic $10^{48}-10^{52}\,$ergs 
      \onslide<3->{\item 1000s detected, $\sim 1$ per day}
      \onslide<4->\item Far away: $z\approx 9.4 \sim 13\,$billion light years!
      \onslide<5->\item Afterglow from X-rays to radio \\
      over timescales of hours to months
      \onslide<6->\item Two types: short and long
      \onslide<7->{\item Short GRBs:\\ 
      mergers of binary neutron stars\\
      \red{GW170817}-\bl{GRB170817A}}
    \end{itemize}
  \end{small}
  \begin{tikzpicture}[overlay,remember picture]
      \onslide<2>\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(3.9cm,1.4cm)}]current page.center) {\includegraphics[height=3.5cm]{figs/GRB_spectrum.jpg}};    
      \node[anchor=center,scale=0.5,opacity=1] at ([shift={(4.5cm,1.cm)}]current page.center) { Mon.Not.Roy.Astron.Soc. 433 (2013) 2739};
      \onslide<3>\node (img1 )[anchor=center,scale=0.8,opacity=1] at ([shift={(3.8cm,0.9cm)}]current page.center) {\includegraphics[height=3.5cm]{figs/Fermi_GRB_sky2.png}};  
      \node[anchor=center,scale=0.5,opacity=1] at ([shift={(5.5cm,1.9cm)}]current page.center) {NASA/Fermi};
      \onslide<4>\node (img2 )[anchor=center,scale=1,opacity=1] at ([shift={(3.6cm,-0.15cm)}]current page.center) {\includegraphics[height=3.8cm]{figs/GRB_vs_redshift.png}};  % from:1401.5069
      \node[anchor=center,scale=0.5,opacity=1] at ([shift={(4.cm,1.4cm)}]current page.center) {Astrophys.J.Suppl. 211 (2014) 12};
      \onslide<5>\node (img3 )[anchor=center,scale=1,opacity=1] at ([shift={(3.4cm,-1.5cm)}]current page.center) {\includegraphics[height=3.5cm]{figs/GRB_afterglow.jpg}}; 
      \onslide<6->\node (img4 )[anchor=center,scale=1,opacity=1] at ([shift={(3.2cm,-2.5cm)}]current page.center) {\includegraphics[height=3.5cm]{figs/GRB_burst_durations.jpg}};
      \node[anchor=center,scale=0.5,opacity=1] at ([shift={(2.cm,-1.2cm)}]current page.center) {NASA/GSFC};
    \end{tikzpicture}
\end{frame}

\begin{frame}{Neutron Stars}{Most extreme stars in the universe}  
  \begin{small}
    \begin{itemize}
      \item Core-collapse supernova remnants
      \item Mass: $\sim M_\odot$ to $3 M_\odot$
      \item Very \red{compact}: radius $\sim 9$ to 15\,km
      \onslide<2->\item High spins: up to 700 times/second
      \onslide<3->\item Extremely dense: teaspoon $\sim 10^9\,$tons
      \onslide<3->{\item Large magnetic fields: $10^4$ to $10^{11}\,$T}
      \item Hot: surface temperature $10^6\,$K
      \onslide<4->\item Equation of state \\
      Piecewise polytropes
      \[ p = K_i \rho^{\Gamma_i},\quad (\rho_{i-1}\le \rho \le \rho_i) \hspace{8cm}\]
    \end{itemize}
  \end{small}
  \begin{tikzpicture}[overlay,remember picture]
      \onslide<1>
	\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(4.2cm,1.5cm)}]current page.center) {\includegraphics[height=3.2cm]{figs/Core_collapseSXS.jpg}};    
	\node[anchor=center,scale=1,opacity=1] at ([shift={(5.4cm,2.9cm)}]current page.center) {\textcolor{white}{SXS}};
      \onslide<2>\node (img1 )[anchor=center,scale=0.8,opacity=1] at ([shift={(3.8cm,0.9cm)}]current page.center) {\includegraphics[height=6cm]{figs/Millisecond_NS.png}}; 
      \node[anchor=center,scale=0.5,opacity=1] at ([shift={(4.8cm,-1.cm)}]current page.center) {Class.Quant.Grav. 30 (2013) 224003};
      \onslide<3>\node (img2 )[anchor=center,scale=0.8,opacity=1] at ([shift={(3.6cm,0.0cm)}]current page.center) {\includegraphics[height=4cm]{figs/NS_cross_section.png}}; 
      \node[anchor=center,scale=0.6,opacity=1] at ([shift={(4.6cm,-1.5cm)}]current page.center) {Robert Schulze};
       \onslide<4>\node (img3 )[anchor=center,scale=0.8,opacity=1] at ([shift={(2.7cm,-2.5cm)}]current page.center) {\includegraphics[height=5cm]{figs/NS_EOS_Lattimer2012.png}}; 
      \node[anchor=center,scale=0.6,opacity=1] at ([shift={(4.cm,-3.8cm)}]current page.center) {Lattimer arXiv:1305.3510};
    \end{tikzpicture}
\end{frame}

@@

\begin{frame}{Gravitational waves: d.o.f.'s}
$A_{\mu\nu} $ is the polarization tensor.
\begin{itemize}
 \uncover<2->{\item $\{ \bar{h}_{\mu\nu}, A_{\mu\nu} \}$: $4\times4$, symmetric \uncover<3->{$\hspace{1.5cm}\Rightarrow \f{4\times 5}{2}\ \ \ = 10$ d.o.f.}}
 \uncover<4->{\item Gauge condition: $\nabla_\mu \bar{h}^{\mu\nu} =  A_{\mu\nu} k^\nu= 0$ \uncover<5->{$\Rightarrow10-4 = \, 6$ d.o.f.}}
 \uncover<6->{\item Residual gauge freedom \hspace{2.25cm} \uncover<7->{$\Rightarrow 6-4 \ \ = \alert{2}$ \alert{d.o.f.}}}
 \end{itemize}
\uncover<7->{\quad \ Consistent with $\pm 2$ helicities of a \bl{massless} spin 2 boson.\\}
\uncover<8->{$\Rightarrow$ \alert{2} POLARIZATIONS (\alert{transverse}): \uncover<9->{$\begin{array}{l}A_{xx}=-A_{yy} = \red{h_+}  \\ A_{xy}=\ \ A_{yx} = \red{h_\times}  \\ \end{array}$}}
\\

\begin{tikzpicture}[overlay,remember picture]
  \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(-3.5cm,-2.5cm)}]current page.center){\includegraphics[height=2.6cm]{figs/white_box.png}};
  \node (img1 )[anchor=center,scale=1.,opacity=1] at ([shift={(3.5cm,-2.5cm)}]current page.center) {\includegraphics[height=2.6cm]{figs/white_box.png}};
\end{tikzpicture}
\end{frame}

\begin{frame}{Gravitational waves: d.o.f.'s}
$A_{\mu\nu} $ is the polarization tensor.
\begin{itemize}
  {\item $\{ \bar{h}_{\mu\nu}, A_{\mu\nu} \}$: $4\times4$, symmetric {$\hspace{1.5cm}\Rightarrow \f{4\times 5}{2}\ \ \ = 10$ d.o.f.}}
  {\item Gauge condition: $\nabla_\mu \bar{h}^{\mu\nu} =  A_{\mu\nu} k^\nu= 0$ {$\Rightarrow10-4 = \, 6$ d.o.f.}}
  {\item Residual gauge freedom \hspace{2.25cm} {$\Rightarrow 6-4 \ \ = \alert{2}$ \alert{d.o.f.}}}
 \end{itemize}
{\quad \ Consistent with $\pm 2$ helicities of a \bl{massless} spin 2 boson.\\}
{$\Rightarrow$ \alert{2} POLARIZATIONS (\alert{transverse}): {$\begin{array}{l}A_{xx}=-A_{yy} = \red{h_+}  \\ A_{xy}=\ \ A_{yx} = \red{h_\times}  \\ \end{array}$}}
\\
%
\begin{tikzpicture}[overlay,remember picture]
  \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(-3.5cm,-2.5cm)}]current page.center){\animategraphics[loop,controls,height=2.6cm]{12}{GWs_plus-}{0}{20}};
  \node (img1 )[anchor=center,scale=1.,opacity=1] at ([shift={(3.5cm,-2.5cm)}]current page.center) {\animategraphics[loop,controls,height=2.6cm]{12}{GWs_cross-}{0}{20}};
\end{tikzpicture}
\end{frame}

%  Two of the same slide next for the right transition effects %%%%%%%%%%%%%%%%%%%%%%%

 \begin{frame}{Making gravitational waves}{non-spherical, accelerated motion}
  \alert{Inspirals}, GRBs, bumps on neutron stars, supernovae, the Big Bang. \\%  (BICEP 2).\\
  Gravitational-wave luminosity: \alert{quadrupole} radiation (leading-order)
  \begin{center} $ \boxed{\dot{E}=L_\text{GW} = \f{G}{c^5} \langle (\partial_t^3 \bar{Q}_{ij})^2 \rangle}$\\
  \vspace{2mm}
  \begin{small}$ \quad \bar{Q}_{ij} = Q_{ij}-\frac{1}{3}\delta_{ij}Q^k_k, \quad Q^{ij} = \int \rho(t,{\mathbf x})x^i x^j d^3 x $ \end{small} \end{center}
  \textcolor{white}{{\bf Binary systems:} 2 points masses in circular orbit.}
  \begin{tikzpicture}[overlay,remember picture]
    \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(-3.8cm,-2.7cm)}]current page.center) {\includegraphics[height=2.9cm]{figs/white_box.png}};
  \end{tikzpicture}
\end{frame}

\begin{frame}{Making gravitational waves}{non-spherical, accelerated motion}
  \alert{Inspirals}, GRBs, bumps on neutron stars, supernovae, the Big Bang. \\%  (BICEP 2).\\
  Gravitational-wave luminosity: \alert{quadrupole} radiation (leading-order)
  \begin{center} $ \boxed{\dot{E}=L_\text{GW} = \f{G}{c^5} \langle (\partial_t^3 \bar{Q}_{ij})^2 \rangle}$\\
  \vspace{2mm}
  \begin{small}$ \quad \bar{Q}_{ij} = Q_{ij}-\frac{1}{3}\delta_{ij}Q^k_k, \quad Q^{ij} = \int \rho(t,{\mathbf x})x^i x^j d^3 x $ \end{small} \end{center}
  {\bf Binary systems:} 2 points masses in circular orbit.
  \begin{tikzpicture}[overlay,remember picture]
    \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(-3.8cm,-2.7cm)}]current page.center) {\animategraphics[loop,controls,height=2.9cm]{12}{Circ_Orb-}{0}{20}};
    %\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(-3.8cm,-2.7cm)}]current page.center) {\includegraphics[height=2.9cm]{figs/white_box.png}};
    \onslide<2->\node (t1 )[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-1.3cm)}]current page.center) {$\mu=m_1 m_2/M^2,\ x(t) = r \cos\Omega t, \ y(t) = r \sin\Omega t $};
    \onslide<3->\node (t2 )[anchor=center,scale=1,opacity=1] at ([shift={(2.25cm,-2.2cm)}]current page.center) {$ Q^{ij} =  2 M\, x^i x^j, \qquad \boxed{\dot{E} = \f{32}{5}\f{G\mu^2}{c^5}r^4 \Omega^6}$};
    \onslide<4->\node (t3 )[anchor=center,scale=1,opacity=1] at ([shift={(2.5cm,-3.2cm)}]current page.center) {Enhancement due to \bl{$e$} (Peters \& Mathews).};
    \node (t3 )[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-4cm)}]current page.center) {$ \bl{\f{\left(1 + \f{73}{24}e^2+ \f{37}{96} e^4 \right)}{(1-e^2)^{7/2}}}$};
  \end{tikzpicture}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{frame}{Compact Binary Inspirals}{Newtonian evolution}
 Define \bl{chirp mass} \hspace{1.cm} $\red{M_c} \equiv \mu^{3/5} M^{2/5} = \tfrac{(m_1 m_2)^{3/5}}{(m_1+m_2)^{1/5}}$ \\
 %and symmetric mass ratio\qquad $\nu \equiv \tfrac{\mu}{M} =\tfrac{m_1 m_2}{M^2}$\\
 \vspace{1mm}
  which gives, via Kepler's \bl{third law}: $\Omega^2 = G M r^{-3}=\omega^2/4$,   
 \onslide<2->
 {
  \begin{footnotesize}
  $$ \boxed{\dot{E} = \f{32}{5}\f{c^5}{G} \left(\f{G M_c\, \omega}{2c^3}\right)^{10/3}}$$
  \end{footnotesize}\\
 } 
%
  \onslide<3->
  {
    {\bf Key idea:} \red{energy balance} between $\dot{E}$ and $\dot{E}_b$\\
    %of gravitational binding energy
    \quad where $ E_b= -\tfrac{G m_1 m_2}{2r} = -\left(\tfrac{G^2 M_c^5 \omega^2}{32}\right)^{1/3} $
  }
%
  \onslide<4->
  {
    \[ 
    \dot{E}(f) = -\dot{E}_b(f) \Longrightarrow \boxed{\red{\dot{f}} = \f{96}{5}\pi^{8/3} \f{(G M_c)}{c^5}^{5/3}\, \red{f^{11/3}} }
    \]
    \[
    \red{ \dot{f} \propto f^{11/3}\quad(1)}
    \]
    \begin{tikzpicture}[overlay,remember picture]
    \node[draw, red,thick,minimum width=3cm,minimum height=0.75cm] (b) at (5.9,0.85){};
    \end{tikzpicture}
  }

@@

\begin{frame}{Compact Binary Inspirals}
  \vspace{-3mm}
  Integrate $\dot{f} \sim f^{11/3} \quad \Longrightarrow \quad \int dt \sim \int f^{-11/3}df \quad\Rightarrow\quad t \sim \red{f^{-8/3}}$
  \\
  \vspace{1mm}
  Fix integration constant $\tau = t_\text{coal} - t >0$. \\
  \vspace{2mm}
  Introduce \red{inspiral time}, i.e, time to \bl{coal}escence
  %
  \begin{small}
  \begin{align}
  \red{\tau_\text{insp}(f)} %&= \f{5}{256\pi}\f{c^5}{(\pi G M_c)^{5/3}} \,{f^{-8/3}}\nn\\
  &\simeq \bl{16.72\,\text{minutes}} \, \left(\f{1.219 M_\odot}{M_c}\right)^{5/3}\,{\left(\f{10\,\text{Hz}}{\red{f}}\right)^{\red{8/3}}\quad \red{(2)}}\nn\hspace{2.7cm}
  \end{align}
  \end{small}
  \\
  \onslide<2->
  {
    Number of GW cycles to coalescence: $\int \tfrac{f}{\dot{f}}df\sim \red{f^{-5/3}}$ %$\int df {f}/\dot{f}$
    \begin{small}
    \begin{align}
    \red{\mathcal{N}_\text{cyc}(f)} %&=\f{1}{32\pi} \f{c^5}{(\pi G M_c)^{5/3}}\left[ f^{-5/3}-f_\text{max}^{-5/3}\right]\nn \\
    &\approx 1.605\times \bl{10^4}\,\left(\f{1.219 M_\odot}{M_c}\right)^{5/3}{ \left(\f{10\,\text{Hz}}{\red{f}} \right)^{\red{5/3}}}\quad \red{(3)}\nn\hspace{3.2cm}
    \end{align}
    \end{small}
  }
  %
  \onslide<3->
  {
    \begin{tikzpicture}[overlay,remember picture]
      \node[draw, red,thick,minimum width=9.2cm,minimum height=1.3cm] (b) at (4.2,3.35){};
      \node[draw, red,thick,minimum width=9cm,minimum height=1.3cm] (b) at (4.1,1){};
      \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(3.9cm,-3.2cm)}]current page.center) {\includegraphics[height=3.5cm]{figs/R_of_Tau.pdf}};
    \end{tikzpicture}
    %
    \[ 
    \tfrac{\dot{r}}{r}\sim \tfrac{\dot{f}}{f} \Longrightarrow \red{r(\tau)}=r_i \left(\f{\red{\tau}}{\tau_i}\right)^{\red{1/4}} \hspace{4cm}
    \]
  }
\end{frame}

\begin{frame}{Gravitational waves from BNS}
  TT gauge, multipole, slow-velocity expansions give 
  \begin{small}
    \[
    h_{ij}^\text{TT} = \tfrac{2}{D}\tfrac{G}{c^4} \ddot{Q}_{ij}^\text{TT}\hspace{6cm}
    \]
    %
    \vspace{-5mm}
    \uncover<2->
    {
      \begin{align*}
      h_+(t) &= h_c(t)\, \left(\f{1+\cos^2\iota}{2}\right)\, \cos[\Phi(t)],\hspace{5cm}\\
      h_\times(t) & =h_c(t)\,\cos\iota \sin[\Phi(t)],
      \end{align*}
    }
  \end{small}
  %
  %
  \uncover<2->{$\iota =\,$ orbital \bl{inclination}}
  \vspace{-3mm}
  %
  \uncover<3->
  {
    \begin{small}
      \begin{align*}
      h_c(t) %&=\f{4}{D}\left(\f{G M_c}{c^2}\right)^{5/3}\, \left(\f{\pi f(t)}{c}\right)^{2/3}\nn\\
      &\approx 1.9\times \bl{10^{-23}} \left(\f{40\,\text{Mpc}}{D}\right)\left(\f{M_c}{1.219 M_\odot}\right)^{5/3}\left(\frac{\red{f}}{10\,\text{Hz}}\right)^{\red{2/3}} \\
      \Phi(t) &=\int_{t_i}^t dt' \omega(t') + \text{PN}
      \end{align*}
    \end{small}
    \\
  }
  %
  \uncover<4->
  {
    Frequency increases as $f^{11/3}$\\
    Amplitude increases as $f^{10/3} $
  }  
  %
  %
  \uncover<2->
  {
    \begin{tikzpicture}[overlay,remember picture]
      \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(3.5cm,1.2cm)}]current page.center) {\includegraphics[height=3cm]{figs/orbit_inc.png}};
      \node[anchor=center,scale=0.5,opacity=1] at ([shift={(3.7cm,-0.1cm)}]current page.center) {\textcolor{white}{\url{www.handprint.com/ASTRO/bineye3.html}}};
      \node (img1 )[anchor=center,scale=1,opacity=1] at ([shift={(2.7cm,-3.2cm)}]current page.center) {\includegraphics[height=2.5cm]{figs/white_box.png}};
      \node[anchor=center,scale=1.4,opacity=1] at ([shift={(1cm,-2.4cm)}]current page.center) {\href{https://www.youtube.com/watch?v=CH9JSqUfnSw}{\textcolor{white}{Chirp!}}};
    \end{tikzpicture}
  }
  \uncover<5->
  {
      \begin{tikzpicture}[overlay,remember picture]
      \node (img1 )[anchor=center,scale=1,opacity=1] at ([shift={(2.7cm,-3.2cm)}]current page.center) {\includegraphics[height=2.5cm]{figs/Chirp.pdf}};
      \node[anchor=center,scale=1.4,opacity=1] at ([shift={(1cm,-2.4cm)}]current page.center) {\href{https://www.youtube.com/watch?v=CH9JSqUfnSw}{\red{Chirp!}}};
    \end{tikzpicture}
  }  
\end{frame}

@@

\begin{frame}{Case study: GW170817}

\begin{frame}{GW Astronomy in the 2020s}

\begin{frame}{GW Astronomy in the 2030s}{The era of Einstein Telescope}
